quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-22 paper-quollr.Rmd
Simplify the fuctions to do small tasks

use_python("~/miniforge3/envs/pcamp_env/bin/python")
use_condaenv("pcamp_env")

reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_PacMAP_code.py"))
reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_TriMAP_code.py"))

@@

@@

# Compute the horizontal spacing (dx) and vertical spacing (dy) between hexagon centers
dx <- sqrt(3) * hex_size
dy <- 1.5 * hex_size

x_length <- 1
y_length_scaled <- diff(range(s_curve_noise_umap$UMAP2))

@@

```{r}
full_grid_centroids_with_hexbin_id <- hex_grid |>
  dplyr::select("c_x", "c_y", "hexID") |>
    dplyr::distinct()

ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  coord_fixed()
```

@@

```{r}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, full_grid_centroids_with_hexbin_id)
```

@@

```{r}
df_with_std_counts <- compute_std_counts(nldr_df = s_curve_noise_umap_with_id)
```

@@

```{r}
hex_full_count_df <- generate_full_grid_info(hex_grid, df_with_std_counts)
```

>>>>

# use_python("~/miniforge3/envs/pcamp_env/bin/python")
# use_condaenv("pcamp_env")
# 
# reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_PacMAP_code.py"))
# reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_TriMAP_code.py"))

@@

# y_min <- 0
# y_max <- sqrt(3)/2

@@

# Compute the horizontal spacing (dx) and vertical spacing (dy) between hexagon centers
# dx <- sqrt(3) * hex_size
# dy <- 1.5 * hex_size

# x_length <- 1
# y_length_scaled <- diff(range(s_curve_noise_umap$UMAP2))

@@

```{r}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  coord_fixed()
```

@@

```{r}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, hex_grid)
```

@@

```{r}
df_with_std_counts <- compute_std_counts(nldr_df_with_hex_id = s_curve_noise_umap_with_id)
```

@@

```{r}
hex_full_count_df <- generate_full_grid_info(nldr_df = s_curve_noise_umap, hex_grid)
```

### 2024-02-22 paper-quollr.tex
Simplify the fuctions to do small tasks

use_python("~/miniforge3/envs/pcamp_env/bin/python")
use_condaenv("pcamp_env")

reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_PacMAP_code.py"))
reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_TriMAP_code.py"))
\end{verbatim}

@@

\begin{verbatim}
full_grid_centroids_with_hexbin_id <- hex_grid |>
  dplyr::select("c_x", "c_y", "hexID") |>
    dplyr::distinct()

ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  coord_fixed()
\end{verbatim}

@@

\begin{verbatim}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, full_grid_centroids_with_hexbin_id)
\end{verbatim}

@@

\begin{verbatim}
df_with_std_counts <- compute_std_counts(nldr_df = s_curve_noise_umap_with_id)
\end{verbatim}

@@

\begin{verbatim}
hex_full_count_df <- generate_full_grid_info(hex_grid, df_with_std_counts)
\end{verbatim}

>>>>

# use_python("~/miniforge3/envs/pcamp_env/bin/python")
# use_condaenv("pcamp_env")
# 
# reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_PacMAP_code.py"))
# reticulate::source_python(paste0(here::here(), "/scripts/function_scripts/Fit_TriMAP_code.py"))
\end{verbatim}

@@

\begin{verbatim}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  coord_fixed()
\end{verbatim}

@@

\begin{verbatim}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, hex_grid)
\end{verbatim}

@@

\begin{verbatim}
df_with_std_counts <- compute_std_counts(nldr_df_with_hex_id = s_curve_noise_umap_with_id)
\end{verbatim}

@@

\begin{verbatim}
hex_full_count_df <- generate_full_grid_info(nldr_df = s_curve_noise_umap, hex_grid)
\end{verbatim}
